---
title: "Final Work"
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
    highlight: zenburn
    fig_height: 4
    fig_width: 6
  html_document:
    code_folding: hide
    highlight: zenburn
    toc: yes
    toc_depth: 3
---

```{r, include=FALSE}
library(plyr)
library(dplyr)
library(knitr)
library(ggplot2)
library(plotly)
library(readxl)
library(stringr)
library(zoo)
library(tidyverse)
```
# 1. Part I : Short and Simple
## 1.1. AI Hype

* AI Hype comes with many advantages. In several years AI will dominate human life by forecasting best economic actions, 
proposing next best-action (in almost every life-action), early-diagnosing many ilnesses and optimizing production chains.
In my opinion the most and the best outcome of AI is minimizing the human error. Especially in health sector automated and
intelligent robots may practise surgeries that is currently imposible. This can really extend human-life. But there is a huge
risk about massive unemployment.

* The human source is the key to develop AI. Well-educated engineers with high mental-capacity are required. In turkey however
there is really huge capacity, current education system can not enchance the students with brand-new technologies. As a person that
his brother working in America for 15 years, our country does not offer good opportunities. If we consider a sufficient level 100,
turkey's level can only be 20. According to WIPO's official figure, AI patenting numbers there is no Turkish Company or Turkish University
in the list. This is a huge and frustrating evidence.

## 1.2. Exploratory Data Analysis Workflow

* My very first step to EDA is analyzing statistics of data (like mean, median, std) and detect outliers. By these statistics we can find
data anomalies to fix. To detect ourliers box plotting is a very good tool. Then we can analyze variables. Categoric (ordinal/nominal) 
variables' frequencies and distribution, numerical (discrete/continous) variables' tendency may give an idea. Histograms and boxplotting 
is very common to analyze distributions. ggplot and plotly libraries area my favorites. 
* In donations sample I assume that we have current category (like education level) levels and people distribution according to levels. 
Maximum number of human access could be my main goal. I think donations should be distributed based on this. Also lowest levelled categories
can be prioritiezed.
* If I was more inclined for a policy, I would try to use data to support my thesis. I think we could find some guiding data for this perspective.
Honesty would not be my priority. But if there is evidence that refuses my thesis, I am going to change it honestly(!) 

## 1.3. Diamonds Analysis

* We see that cut property is very important for carat price. 

```{r}
my_diamond <- diamonds %>% mutate(carat_price=price/carat) %>% group_by(color, cut) %>% 
  summarise(mean_carat_price =mean(carat_price)) %>% arrange(desc(mean_carat_price))
ggplot(my_diamond, aes(x=cut, y=mean_carat_price, fill=cut)) + geom_boxplot() + 
  labs(x="Diamond Cut", y="Carat Price",title="Diamond Cut vs Carat Price", fill = "Cut")
```

# 2. Part II: Extending Our Group Project

```{r, echo=FALSE}
get_data_url <- function(start_year) {
  data_url <- paste("https://github.com/pjournal/mef03g-mujde-r/blob/master/Group%20Project/Raw%20Data/", start_year, "-",
                    start_year + 1, ".csv?raw=true", sep='')
  return (data_url)
}

get_data_between_years <- function (start_year, end_year){
all_raw_data <- data.frame()
  for (year in seq(start_year, end_year)) {
    data_url <- get_data_url(year)
    raw_data <- read.csv(data_url,skip=1,sep=',',header=F)
    raw_data <- raw_data %>% mutate(V1 = year)
    if(year < 1999){
      all_raw_data <- rbind.fill(all_raw_data, raw_data)
    } else if(year < 2017){
      ## First 10 variables
      all_raw_data <- rbind.fill(all_raw_data, raw_data[c(1:10)])
    } else{
      ## First 22 variables
      all_raw_data <- rbind.fill(all_raw_data, raw_data[c(1:22)])
    }
  }
  return (all_raw_data)
}
raw_data <- get_data_between_years(1994, 2018)
colnames(raw_data)<-c("season","date","HomeTeam","AwayTeam","FTHG","FTAG","FTR","HTHG","HTAG","HTR","HS","AS","HST","AST","HF","AF","HC","AC","HY","AY","HR","AR")
```
```{r}
most_common_match_results <- raw_data %>% unite(match_score,c(FTHG, FTAG), sep="-") %>% select(season, match_result = FTR, match_score) 
most_common_match_results <- most_common_match_results %>% group_by(match_result, match_score) %>% 
  summarise(count=n()) %>% top_n(5, wt=count)

common_home_win <-most_common_match_results %>% filter(match_result == "H")
common_away_win <-most_common_match_results %>% filter(match_result == "A")
common_draw <- most_common_match_results %>% filter(match_result == "D")
```

## 2.1. Home Win Most Common Match Scores

```{r}
ggplot(common_home_win, aes(reorder(match_score, count), count, fill=match_score)) +geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + coord_polar() +
  labs(x="Score", y="Count", title="Most common Match Scores of Home Win", fill="Score")
```

## 2.2. Away Win Most Common Match Scores

```{r}
ggplot(common_away_win, aes(reorder(match_score, count), count, fill=match_score)) +geom_bar(stat="identity")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + coord_polar() +
    labs(x="Score", y="Count", title="Most common Match Scores of Away Win", fill="Score")
```

## 2.3. Draw Most Common Match Scores

```{r}
ggplot(common_draw, aes(reorder(match_score, count), count, fill=match_score)) +geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + coord_polar() +
    labs(x="Score", y="Count", title="Most common Match Scores of Draw", fill="Score")
```

# 3. Welcome to Real Life
## 3.1. Data Preparation
```{r, echo=TRUE, message=FALSE, include=FALSE}
all_data <- data.frame()
for (start_year in seq(2014,2018)){
 data_url <- paste("https://github.com/pjournal/mef03-Demirefe91/blob/master/",start_year,"_Organik_Tarimsal_Uretim_Verileri.xlsx?raw=true",sep="")
  tmp<-tempfile(fileext=".xlsx")
  download.file(data_url,destfile=tmp, mode='wb')
  raw_data<-readxl::read_excel(tmp,col_names = FALSE, skip=4)
  ## year added
  raw_data <-  raw_data %>% mutate(V9 = start_year)
  all_data <- rbind.fill(all_data, raw_data)
}
colnames(all_data) <- c("sehir", "urun", "sayı", "uretim", "toplama", "nadas", "toplam", "miktar", "yil")
## special characters encoding
all_data$sehir <- iconv(all_data$sehir, from = 'UTF-8', to = 'ASCII//TRANSLIT')
## convert sehir information to same format
all_data$sehir <- tolower(all_data$sehir)
## fill N/A sehir values from previous value
all_data$sehir <- na.locf(all_data$sehir)
## convert tons into kilograms
all_data <- all_data %>% mutate(miktar=as.integer(miktar*1000))
## special characters encoding
all_data$urun <- iconv(all_data$urun, from = 'UTF-8', to = 'ASCII//TRANSLIT')
## convert urun information to same format
all_data$urun <- tolower(all_data$urun)
```

```{r}
## total city values extracted into total_data
total_data <- all_data %>% filter(str_detect(sehir,"toplam") & !str_detect(sehir,"genel") & !str_detect(sehir,"not"))
total_data$sehir <- gsub('toplam ', '', total_data$sehir)
total_data <- total_data %>% select(sehir, yil, sayi, uretim, toplama, nadas, toplam, miktar)

## city detail values extracted into all_data
all_data <- all_data %>% filter(!str_detect(sehir,"toplam")) %>% select(sehir, urun, miktar, yil)
glimpse(all_data)
glimpse(total_data)
```

## 3.2. Analyses
### 3.2.1 Gross Production of 10 Top Cities

```{r}
gross_production <- all_data %>% filter(!is.na(miktar)) %>% group_by(sehir) %>% 
  summarise(total_production = sum(miktar / 1000000)) %>%
  arrange(desc(total_production)) %>% head(10)

ggplot(gross_production, aes(reorder(sehir,total_production), total_production, fill=sehir))+
  geom_bar(stat='identity') + coord_flip() + labs(x="City", y="Total Production Gross Ton", fill="City",
        title="Top 10 Productive Cities")
```

* Let's store these cities

```{r}
top_cities <- as.vector(gross_production$sehir)
```

### 3.2.2. Distribution of Real Production / Gathering Area of 10 Top Cities

```{r}
proportion_uretim <- total_data %>% filter(sehir %in% top_cities) %>% group_by(sehir) %>% 
  summarise(total = (sum(uretim)) * 100,  type="production area")
proportion_toplama <- total_data %>% filter(sehir %in% top_cities) %>% group_by(sehir) %>% 
  summarise(total = (sum(toplama)) * 100,  type="gathering area")
proportion_all = bind_rows(proportion_uretim, proportion_toplama)
ggplot(proportion_all, aes(sehir, total, fill=type)) + geom_bar(stat="identity", position="stack") + coord_flip() +
  labs(x="City", y="Total Area (HA)", fill="Area Type", title="Production Area Distribution of 10 Top Cities")
```

### 3.2.3 Poduction Variety of Top 5 Cities By Years

```{r}
variety <- all_data %>% filter(miktar > 0) %>% group_by(yil, sehir) %>% summarise(count=n()) %>% top_n(5, wt=count)
variety_cities <- as.vector(variety$sehir)
top_variety <- all_data %>% filter(sehir %in% variety_cities)

ggplot(top_variety, aes(sehir, fill=sehir)) + geom_density() + facet_wrap(~yil) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(x="City", fill="City", title="Production Variety of Cities")
```

### 3.2.4 Most Nonfertile City Records

```{r}
fertility <- total_data %>% filter(!is.na(nadas) & nadas > 0 & !is.na(toplam) & toplam > 0 ) %>%
  transmute(city = sehir,  percentage= (nadas/toplam) * 100, non_fertile_area=nadas, total_area=toplam, year=yil) %>%
  arrange(desc(non_fertile_area)) %>% head(10)
fertility
```



